Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-10-08 draft_lm1.tex
minor improvements

To elicit priors for the $p_i \sim Be(a,b)$, we used the proportion of 
serotyped cases at the end of each epidemic as the expected value for the $p_i$.

Let $S_{0T}$ and $S_{fT}$, be the total number of susceptibles before and 
after an epidemic, respectively

>>>>

Initially, we have no information about the distribution of the $p_i$ but they 
can be learned gradually with each epidemic.

Let $S_{0T}$ and $S_{fT}$, be the total number of susceptibles before and 
after an epidemic, respectively. The total number of cases observed in an 
epidemic, $I_T = \sum_i I_i$ can be expressed as $S_{0T}-S_{fT}$, thus
\begin{align}
 S_{fT} &= S_{0T} - I_T\\
 &=\sum S_i - \sum I_i\\
 &=\sum_i S_i-I_i
\end{align}

If $S_i/n \approx p_i$ and $I_i$ is observed, we can adjust the initial 
$p_i$ proportionately to $I_i$.
\todo[inline]{sera que da para fazer inferencia bayesiana aqui?}
